\textsf{Are large language models superhuman chemists?}

### 2024-10-18 src/tex/ms.tex
updated arxiv references

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of these models has led to a rapid increase in their capabilities,\autocite{brown2020language,zhong2024benchmarking} with the leading models now being able to pass in some evaluations the United States Medical Licensing Examination.\autocite{kung2023performance} 
They also have been shown to design and autonomously perform chemical reactions when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4, Boiko_2023, bran2023chemcrow}
While some see \enquote{sparks of \gls{agi}} in them,\autocite{bubeck2023sparks} others consider them as \enquote{stochastic parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
Nevertheless, the promise of these models is that they have shown the ability to solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier, ai4science2023impact}
This has led to tremendous economic interest and investment in such generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}

Chemists and materials scientists have quickly caught on to the mounting attention given to \glspl{llm}, with some voices even suggesting that \enquote{the future of chemistry is language}.\autocite{White_2023}
This statement is motivated by a growing number of reports that use \glspl{llm} to predict properties of molecules or materials,\autocite{jablonka202314, jablonka2024leveraging, xie2024fine, liao2024words, zhang2024chemllm, zhong2024benchmarking}  optimize reactions\autocite{ramos2023bayesian, kristiadi2024sober}  generate materials,\autocite{rubungo2023llm, flam2023language, gruver2024fine} extract information,\autocite{Patiny_2023, Dagdelen_2024, Zheng_2024, lala2023paperqa, caufield2023structured, gupta2022discomat} or to even prototype systems that can autonomously perform reactions in the physical world based on commands provided in natural language.\autocite{bran2023chemcrow, Boiko_2023, darvish2024organa}

>>>>

\clearpage
\begin{refsection}
\section{Introduction}
\Glspl{llm} are \gls{ml} models trained on massive amounts of text to complete sentences. 
Aggressive scaling of these models has led to a rapid increase in their capabilities,\autocite{brown2020language,zhong2024benchmarking} with the leading models now being able to pass in some evaluations the United States Medical Licensing Examination.\autocite{kung2023performance} 
They also have been shown to design and autonomously perform chemical reactions when augmented with external tools such as web search and synthesis planners.\autocite{openai2024gpt4, Boiko_2023, bran2023chemcrow, darvish2024organa}
While some see \enquote{sparks of \gls{agi}} in them,\autocite{bubeck2023sparks} others consider them as \enquote{stochastic parrots}---i.e., systems that only regurgitate what they have been trained on.\autocite{bender2021dangers}
Nevertheless, the promise of these models is that they have shown the ability to solve a wide variety of tasks they have not been explicitly trained on.\autocite{bommasani2021opportunities, anderljung2023frontier, ai4science2023impact}
This has led to tremendous economic interest and investment in such generative models, with an expected market of more than \$1.3 trillion (almost \$30 billion for drug discovery applications) by 2032.\autocite{bloomberg}

Chemists and materials scientists have quickly caught on to the mounting attention given to \glspl{llm}, with some voices even suggesting that \enquote{the future of chemistry is language}.\autocite{White_2023}
This statement is motivated by a growing number of reports that use \glspl{llm} to predict properties of molecules or materials,\autocite{jablonka202314, jablonka2024leveraging, xie2024fine, liao2024words, zhang2024chemllm, zhong2024benchmarking}  optimize reactions\autocite{ramos2023bayesian, kristiadi2024sober}  generate materials,\autocite{rubungo2023llm, flam2023language, gruver2024fine, alampara2024mattextlanguagemodelsneed} extract information,\autocite{Patiny_2023, Dagdelen_2024, Zheng_2024, lala2023paperqa, caufield2023structured, gupta2022discomat, schillingwilhelmi2024textinsightlargelanguage, skarlinski2024language} or to even prototype systems that can autonomously perform reactions in the physical world based on commands provided in natural language.\autocite{bran2023chemcrow, Boiko_2023, darvish2024organa}
